### 2018-11-29 2018_nips_vigil_poster/main.tex
final update vigil

\documentclass[final,paperwidth=36in,paperheight=48in,portrait,fontscale=0.35]{baposter}
% NIPS Workshops format

@@

	\texttt{\{vmarois,jayram,tkornut,byounes,asozcan\}@us.ibm.com},{\{vincent.albouy\}@ibm.com}\\
  }
  { % Left Eye Catcher
\includegraphics[width=4cm]{../img/arc_logo.png}
  }

@@

		\includegraphics[width=0.35\textwidth]{../img/mac_cell.pdf}
		\label{subfig:pendulum_picture}
		\caption{The MAC cell ~\cite{hudson2018compositional}}
		\label{fig:pendulum}
	\end{figure}

\begin{description}
	\item[$\bullet$] The MAC network is a recurrent model that performs sequential reasoning; at each step the model analyzes the question and shifts the attention over the image
	\item[$\bullet$] The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
	\item[$\bullet$] The input unit uses an LSTM to process the question in a word-by-word manner producing a sequence of contextual words and a final question representation.
	\item[$\bullet$] The input unit utilizes a pre-trained ResNet followed by two CNN layers to extract a feature map  from the image.

@@

	Our proposed modification to the MAC network is based on two heuristic simplifications of the
	MAC cell:

@@

\noindent\textbf{Read and write units:}
\begin{multicols}{2}
	\noindent
	\begin{align*}
	&I_{ihw} = (W_{m}^{[d \times d]} \mem_{i-1} + b_{m}^{[d]}) \\
	& \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{k}^{[d]}) \tag{r1} \\
	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
	\end{align*}
	\columnbreak
	{\color{Plum}
		\begin{align*}
		&I_{ihw} = \mem_{i-1} \odot \kb_{hw} \tag{r1} \\ \\
		&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
		&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
		&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
		&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
		&\mem_i = W_{rm}^{[d \times 2d]} \rr_i + b_{rm}^{[d]} \tag{w1}
		\end{align*}}
\end{multicols}

@@

\headerbox{Datasets - CLEVR and CoGenT}{name=dataset, column=1}{
The CLEVR task:
		\begin{figure}[H]
		\centering
		\includegraphics[width=0.33\textwidth]{../img/teaser.jpg}
	    \end{figure}

@@

CLEVR \& CoGenT accuracies for the MAC \& S-MAC models:
	\begin{table}[H]
	\centering
	\scalebox{0.9}{
	\begin{tabular}{lllllllll}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & (a) \\
		\cmidrule{1-8}
		\cmidrule{1-8}

@@

	\begin{figure}[H]
	\centering
	\subfloat[]{{
			\includegraphics[width=0.6\textwidth]{../img/fail_mac_cogent_b_shape.png}
			\label{subfig:pendulum_picture}
	}}
	\label{fig:fail_mac_shape}

>>>>

\documentclass[final,paperwidth=36in,paperheight=48in,portrait,fontscale=0.36]{baposter}
% NIPS Workshops format

@@

	\texttt{\{vmarois,jayram,tkornut,byounes,asozcan\}@us.ibm.com},{\{vincent.albouy\}@ibm.com}\\
  }
  { % Left Eye Catcher

\includegraphics[width=4cm]{../img/arc_logo.png}

@@

		\includegraphics[width=0.33\textwidth]{../img/mac_cell.pdf}
		\label{subfig:pendulum_picture}
		\caption{The MAC cell ~\cite{hudson2018compositional}}
		\label{fig:pendulum}
	\end{figure}

\begin{description}
	\item[$\bullet$] The MAC network is a recurrent model that performs sequential reasoning; at each step the model analyzes the question and shifts the attention over the image
	\item[$\bullet$] The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
	\item[$\bullet$] The input unit uses an LSTM to process the question  and CNN layers to extract a feature map  from the image.

@@

	Our proposed modification to the MAC network is based on two heuristic simplifications:

@@

\noindent\textbf{Read and write units:}
\begin{multicols}{2}
	\noindent
	\begin{align*}
	&I_{ihw} = (W_{m}^{[d \times d]} \mem_{i-1} + b_{m}^{[d]}) \\
	& \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{k}^{[d]}) \tag{r1} \\
	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
	\end{align*}
	\columnbreak
	{\color{Plum}
		\begin{align*}
		&I_{ihw} = m _{i-1} \odot k _{hw} \tag{r1} \\ 
		&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
		&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
		&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
		&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
		&\mem_i = W_{rm}^{[d \times 2d]} \rr_i + b_{rm}^{[d]} \tag{w1}
		\end{align*}}
\end{multicols}

@@

\headerbox{Links}{name=links,column=0,below=data acquisition}{
	\footnotesize
	\begin{center}
		\begin{tabular}{cc} 
			\includegraphics[height=1.6 cm]{../img/github_repo_qr_code.png} &
			\includegraphics[height=1.6 cm]{../img/doc_qr_code.png}  &
			Github &  Reproducibility \\
			repository & documentation
		\end{tabular}
	\end{center}
}

\headerbox{Datasets - CLEVR and CoGenT}{name=dataset, column=1}{
The CLEVR task:
		\begin{figure}[H]
		\centering
		\includegraphics[width=0.35\textwidth]{../img/teaser.jpg}
	    \end{figure}

@@

CLEVR \& CoGenT accuracies for the MAC \& S-MAC models:
	\begin{table}[H]
	\centering
	\scalebox{1}{
	\begin{tabular}{lllllllll}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & (a) \\
		\cmidrule{1-8}
		\cmidrule{1-8}

@@

	\begin{figure}[H]
	\centering
				\includegraphics[width=0.65\textwidth]{../img/fail_mac_cogent_b_shape.png}
